The Galactic Delay-Time Distribution of Type Ia Supernovae:\\ A Chemical Evolution Perspective

### 2022-08-10 src/tex/ms.tex
[showyourwork] overleaf sync

\usepackage{showyourwork}
\usepackage{amsmath}
\usepackage{siunitx}

% custom unit definitions
\DeclareSIUnit\year{yr}

@@

\begin{deluxetable}{lCl}
\tablecaption{Sources of the various forms of delay time distribution.}
\tablehead{
\colhead{Name} & \colhead{Form} & \colhead{Source}
}
\startdata
Field Galaxy Power-Law      & t^{-1.1}              & \citet{Maoz2017-CosmicDTD} \\   
Galaxy Cluster Power-Law    & t^{-1.4}              & \citet{Maoz2017-CosmicDTD} \\
Short Exponential           & e^{-t/1.5\,\rm{Gyr}}  & \citet{Schonrich2009-RadialMixing} \\
\enddata
\end{deluxetable}

@@

\begin{equation}
    f_{\rm{Ia}}^{\rm{DD}}(t) \propto
    \begin{cases}
        t^{\alpha_1} (1 - A_{\rm{rise}} e^{-t/\tau_{\rm{rise}}}) & t \le \SI{1}{\giga\year} \\
        B t^{\alpha_2} (1 + A_{\rm{tail}} e^{-(t - \SI{1}{\giga\year})/\tau_{\rm{tail}}}) & t > \SI{1}{\giga\year}
    \end{cases}
    \label{eq:greggio05-approx}
\end{equation}

@@

\begin{equation}
    B = \frac{1}{1 + A_{\rm{tail}}} t^{(\alpha_1-\alpha_2)} (1 - A_{\rm{rise}} e^{-(\SI{1}{\giga\year})/\tau_{\rm{rise}}}).
\end{equation}

>>>>

\usepackage{showyourwork}
\usepackage{amsmath}
% \usepackage{siunitx}

% custom unit definitions
% \DeclareSIUnit\year{yr}

@@

\begin{deluxetable}{lCl}
\tablecaption{Sources of the various forms of delay time distribution.}
\tablehead{
\colhead{Name} & \colhead{Form} & \colhead{Source}
}
\startdata
Field Galaxy Power-Law      & t^{-1.1}              & \citet{Maoz2017-CosmicDTD} \\   
Galaxy Cluster Power-Law    & t^{-1.4}              & \citet{Maoz2017-CosmicDTD} \\
Short Exponential           & e^{-t/1.5~\rm{Gyr}}  & \citet{Schonrich2009-RadialMixing} \\
\enddata
\end{deluxetable}

@@

\begin{equation}
    f_{\rm{Ia}}^{\rm{DD}}(t) \propto
    \begin{cases}
        t^{\alpha_1} (1 - A_{\rm{rise}} e^{-t/\tau_{\rm{rise}}}) & t \le 1~\rm{Gyr} \\
        B t^{\alpha_2} (1 + A_{\rm{tail}} e^{-(t - 1~\rm{Gyr})/\tau_{\rm{tail}}}) & t > 1~\rm{Gyr}
    \end{cases}
    \label{eq:greggio05-approx}
\end{equation}

@@

\begin{equation}
    B = \frac{1}{1 + A_{\rm{tail}}} t^{(\alpha_1-\alpha_2)} (1 - A_{\rm{rise}} e^{-(1~\rm{Gyr})/\tau_{\rm{rise}}}).
\end{equation}
